%----------------------------------------------------------------------------------------
%	IPsoft Technical Executive, Team Supervisor Windows
%----------------------------------------------------------------------------------------
\begin{tabularx}{1\linewidth}{>{\raggedleft\scshape}p{2.5cm}X}
\gray Employer & \textbf{IPsoft} \hfill Amsterdam, The Netherlands\\
\gray Job Title & \textbf{Technical Executive, Team Supervisor Windows} \hfill May 2015 --- now\\
\gray Reference & \textbf{Nick Walsh} \\
\end{tabularx}

\vspace{2pt}
IPsoft is a managed service provider, pioneering innovation in the development and delivery of autonomic and cognitive technologies. For IPsoft I'm tasked with a dual role. In the position of Team-Supervisor I'm overseeing the quality of employee performance and creating a motivating workplace. I was also be directly involved with interviewing and hiring of employees.\\
\\
\textbf{Key Contributions:}
\begin{itemize}
\item Leading a team of eight Senior IT engineers and two Junior IT engineers.
\item Overseeing the on-boarding training curriculum. 
\item Conducted over 50 technical job interviews.
\item Grew the team from three to ten IT engineers over one year.
\item Setup a quarterly in-house automation training. 
\item Manage relationships to ensure employee satisfaction.
\item Created KPI's providing management with input about the performance of members of the team. \\
\end{itemize}
In the position of Technical Executive I am responsible for running the day to day IT operations for one of our top clients. Ensuring the organization’s IT technology works efficiently and securely, which is the main goal. The global, multi-site IT environment consists of over 1000 Windows and Linux/Unix servers running on top of 80 plus VMware vSphere/ESXi hosts.\\ 
\\
\textbf{Key Contributions:}
\begin{itemize}
\item Leading a team of 7 Senior IT engineers by training, motivating and setting clear objectives.
\item Building a strong trust and positive relationship with the client. 
\item Written over 50 SOP's to ensure uniform effective processing of requests and incidents.
\item Oversee all technical projects, system and software upgrades. 
\item Building a weekly automation pipeline ensuring maximum autonomic resolution for the client. 
\item Manage relationships with (third party) vendors for technical products and services for the organization.
\item Hosting bi-weekly internal team meetings.
\end{itemize}

\vspace{12pt}

%----------------------------------------------------------------------------------------
%	IPsoft Sr. Windows Engineer
%----------------------------------------------------------------------------------------
\begin{tabularx}{1\linewidth}{>{\raggedleft\scshape}p{2.5cm}X}
\gray Employer & \textbf{IPsoft} \hfill Amsterdam, The Netherlands\\
\gray Job Title & \textbf{Technical Lead, Sr. Windows Engineer} \hfill November 2014 --- April 2015\\
\gray References & \textbf{Michell Grauwmans, Remco Veltrop} \\
\end{tabularx}

\vspace{2pt}
%IPsoft, is a leading managed services provider, offering a complete solution to enterprise customers for outsourcing global Internet operations. IPsoft deploys, manages, secures, scales, and monitors e-business systems using its unique automation technology, which automates functions otherwise done manually; thereby delivering higher quality, cost savings, and increased flexibility. \\

\textbf{Key Contributions:}
\begin{itemize}
\item Diagnosed and re-mediated issues within enterprise sized Windows Server Infrastructure's. 
\item Build and bug-fix over a hundred automatons which either diagnose or completely resolve recurring issues saving my employer many FTE's. Used technologies include  PowerShell, Bash, SQL and JavaScript. 
\item Worked with tier 1 clients to align and support their requirements with a high level of attention and intimacy.
\item Develop automation using PowerShell and JavaScript to automate repetitive tasks in the client environments. 
\item Lead technical projects and deployments improving the client's infrastructure. 
\end{itemize}

\vspace{12pt}


%----------------------------------------------------------------------------------------
%	NS
%----------------------------------------------------------------------------------------
\begin{tabularx}{1\linewidth}{>{\raggedleft\scshape}p{2.5cm}X}
\gray Employer & \textbf{Nederlandse Spoorwegen} \hfill Utrecht, The Netherlands\\
\gray Job Title & \textbf{Active Directory consultant} \hfill October 2013 --- October 2014\\
\gray Reference & \textbf{John de Mol} \\
\end{tabularx}

\vspace{2pt}

NS provides rail services on the Dutch main rail network (hoofdrailnet). 25,000 employees make sure that 4,800 domestic trains run every day. I was hired as an Active Directory consultant to inventory, migrate, clean and decommission Active Directory domains.

\textbf{Key Contributions:}
\begin{itemize}
\item Decommissioned eight Active Directory domains to improve security, reliability and reduce the complexity of the Active Directory domain infrastructure.
\item Automated repetitive Active Directory inventory reports using Microsoft PowerShell, saving my employer 2 FTE's.
\item Developed a tool using PowerShell to detect network and firewall issues between domain controllers across multiple forests.
\item Designed and implemented an Active Directory housekeeping policy to ensure a secure and healthy domain environment.
\item Identified and resolved several LAN and DNS connectivity issues.
\item Consolidated user, computer and group objects across four primary Active Directory domains.
\item Managed Active Directory operations and resolved weekly third-tier technical task tickets using HP Operations Manager.
\end{itemize}

\vspace{12pt}

%----------------------------------------------------------------------------------------
%	Em'bed
%----------------------------------------------------------------------------------------
\begin{tabularx}{1\linewidth}{>{\raggedleft\scshape}p{2.5cm}X}
\gray Employer & \textbf{Em'bed} \hfill Den Haag, The Netherlands\\
\gray Job Title & \textbf{Infrastructure specialist}\hfill September 2013 --- October 2014\\
\gray Reference & \textbf{Maurits van Boetzelaer} \\
\end{tabularx}

\vspace{2pt}

Em'bed is a consultancy firm specializing in identity and access management solutions. In the position of Infrastructure specialist I performed several Active Directory security and health assessments.

\textbf{Key Contributions:}
\begin{itemize}
\item Developed an automated Active Directory and Exchange assessment tool using PowerShell v2.
\item Identified and reported several Active Directory configuration issues for multiple clients.
\end{itemize}

\vspace{12pt}

%----------------------------------------------------------------------------------------
%	Meritor, Inc
%----------------------------------------------------------------------------------------
\begin{tabularx}{1\linewidth}{>{\raggedleft\scshape}p{2.5cm}X}
\gray Employer & \textbf{Meritor, Inc} \hfill Roermond, The Netherlands\\
\gray Job Title & \textbf{Windows engineer} \hfill May 2011 --- September 2012\\
\gray Reference & \textbf{Martijn Tigchelaar} \\
\end{tabularx}

\vspace{2pt}

Meritor, Inc. is a corporation headquartered in Troy, Michigan (USA) which manufactures automobile components for light service vehicles, trucks, and trailers. Meritor is a Fortune 500 company that has 9,000 employees in 18 countries. I was responsible for providing Windows and VMware administration. Also managed network monitoring servers, Active Directory, DNS, Exchange, WSUS and wireless access points (Radius).

\textbf{Key Contributions:}
\begin{itemize}
\item Designed, implemented, and maintained the new Active Directory domain infrastructure supporting 9,000 users.
\item Replaced 50+ Windows 2000 domain controllers with Windows 2003 and Windows 2008R2 domain controllers
\item Migrated DNS, WINS, DHCP, IAS and WSUS services from Windows 2000 servers to new VM's running Windows 2008R2.
\item Managed data center operations and resolved ten daily third-tier technical support tickets using Remedy.
\item Managed, Deployed and maintained 30+ private virtual clouds based on VMWare vSphere 5.0 vCenter v5.0.
\end{itemize}

\vspace{12pt}

%----------------------------------------------------------------------------------------
%	Kempenhaeghe
%----------------------------------------------------------------------------------------
\begin{tabularx}{1\linewidth}{>{\raggedleft\scshape}p{2.5cm}X}
\gray Period & \textbf{May 2011 --- December 2011}\\
\gray Employer & \textbf{Kempenhaeghe} \hfill Heeze, The Netherlands\\
\gray Job Title & \textbf{IT engineer}\\
\gray Supervisor & \textbf{Rob Santegoeds} \\
\end{tabularx}

\vspace{2pt}

Kempenhaeghe is an expertise center for epilepsy and sleep-wake disorders. I monitored and managed over fifty Windows 2003 servers, Active Directory, Exchange and VMWare vSpehere 4.1 infrastructure.

\textbf{Key Contributions:}
\begin{itemize}
\item Troubleshot and resolved up to twenty second-tier Windows-based support issues per week for hundreds of users with an infrastructure of over fifty Windows servers.
\item Created and maintained the company asset inventory for all computer hardware with TopDesk.
\item Maintained company tools, including RSA Tokens, conference systems, and mobile phones.
\end{itemize}

\vspace{12pt}


%----------------------------------------------------------------------------------------
%	Getronics
%----------------------------------------------------------------------------------------

\begin{tabularx}{1\linewidth}{>{\raggedleft\scshape}p{2.5cm}X}
\gray Period & \textbf{January 2011 --- April 2011}\\
\gray Employer & \textbf{Getronics} \hfill Beek, The Netherlands\\
\gray Job Title & \textbf{Service Desk Analyst}\\
\gray Supervisor & \textbf{Claudio Mazzei} \\
\end{tabularx}

\vspace{2pt}
Getronics is a company focused on IT Workspace Management Services. I was an employee within the Managed Services department responsible for resolving over sixty daily first-tier technical support tickets for a large scale client within the financial sector.

\textbf{Key Contributions:}
\begin{itemize}
\item Delivered customer service by registering and analyzing service requests in HP Operations Manager
\item Troubleshot over 36,000 workstations, document scanners, printers, and a IP-based phone system.
\item Topped the monthly charts for handling the most service requests.
\item Performed daily desktop and laptop maintenance.
\end{itemize}

\vspace{12pt}

%----------------------------------------------------------------------------------------
%	Orbis
%----------------------------------------------------------------------------------------

\begin{tabularx}{1\linewidth}{>{\raggedleft\scshape}p{2.5cm}X}
\gray Period & \textbf{August 2009 --- January 2010}\\
\gray Employer & \textbf{Orbis Medical Centre} \hfill Roermond, The Netherlands\\
\gray Job Title & \textbf{Windows engineer}\\
\gray Super Visor & \textbf{Rob Aarts} \\
\end{tabularx}

\vspace{2pt}
Orbis Medisch en Zorgconcern is a High Tech hospital. I was responsible for designing and testing an improvement to the Server Based Computing environment.

\textbf{Key Contributions:}
\begin{itemize}
\item Designed a SBC environment, supporting over 2,000 users, based on Windows Server 2008 R2 Remote Desktop Services, VMWare Thinapp 4.5 and RES PowerFuse 2010.
\item Implemented RES Wisdom work-flows for automated roll-out of new RDS servers.
\item By completely separating the OS, Applications and User profiles we were able to provide a fast and easy to manage SBC environment.
\end{itemize}

\section{Additional IT Experience}

\begin{tabularx}{1\linewidth}{>{\raggedleft\scshape}p{2.5cm}X}
\gray Period & \textbf{May 2013 --- July 2013}\\
\gray Employer & \textbf{SURFnet} \hfill Utrecht, The Netherlands\\
\gray Job Title & \textbf{Researcher}\\
\gray Supervisor & \textbf{Jac Kloots} \\
\end{tabularx}

\vspace{2pt}

I was responsible for visualizing the current state of BGP RPKI. Results have been used by ISP's to improve the security of the BGP routing protocol. Results are automatically generated daily and presented at \url{http://rpki.surfnet.nl}.

\vspace{12pt}

\begin{tabularx}{1\linewidth}{>{\raggedleft\scshape}p{2.5cm}X}
\gray Period & \textbf{January 2013 --- February 2013}\\
\gray Employer & \textbf{NLnet Labs} \hfill Amsterdan, The Netherlands\\
\gray Job Title & \textbf{Researcher}\\
\gray Supervisor & \textbf{Matthijs Mekking} \\
\end{tabularx}

\vspace{2pt}

Researched different mechanisms to defend against DNS amplification attacks. Recommended DNS admins to implement Response Rate Limiting.

\vspace{12pt}

\begin{tabularx}{1\linewidth}{>{\raggedleft\scshape}p{2.5cm}X}
\gray Period & \textbf{October 2012 --- December 2012 (Part Time)}\\
\gray Employer & \textbf{University of Amsterdam} \hfill Amsterdan, The Netherlands\\
\gray Job Title & \textbf{Researcher}\\
\gray Supervisor & \textbf{Jaap van Ginkel} \\
\end{tabularx}

\vspace{2pt}

Discovered a serious weakness in the ABN AMRO mobile banking Android application. A weakness in their SSL implementation allowed us to execute a "Man In The Middle" attack, view account balance and even change transactions.

\vspace{12pt}

\begin{tabularx}{1\linewidth}{>{\raggedleft\scshape}p{2.5cm}X}
\gray Period & \textbf{March 2008 --- December 2010 (Part Time)}\\
\gray Employer & \textbf{Media Markt} \hfill Roermond, The Netherlands\\
\gray Job Title & \textbf{Sales employee}\\
\gray Supervisor & \textbf{Bjorn Mickers} \\
\end{tabularx}

\vspace{2pt}

Sales employee selling computer hardware, software and accessories.

\vspace{12pt}

\begin{tabularx}{1\linewidth}{>{\raggedleft\scshape}p{2.5cm}X}
\gray Period & \textbf{December 2010 --- September 2012}\\
\gray Employer & \textbf{Comprehensive ICT solutions} \hfill Weert, The Netherlands\\
\gray Job Title & \textbf{Technical Consultant}\\
\gray Supervisor & \textbf{Ben Dassen} \\
\end{tabularx}

\vspace{2pt}

IT consultant for a broad range IT projects in the field of Microsoft, VMWare and Citrix.

\vspace{12pt}

\begin{tabularx}{1\linewidth}{>{\raggedleft\scshape}p{2.5cm}X}
\gray Period & \textbf{October 2007 --- March 2008 (Part Time)}\\
\gray Employer & \textbf{Thuiszorg midden-limburg} \hfill Roermond, The Netherlands\\
\gray Job Title & \textbf{Windows system administrator}\\
\gray Supervisor & \textbf{John Schulpen} \\
\end{tabularx}

\vspace{2pt}

System administrator managing Windows Server 2003, Citrix Metaframe XP 3.5 and Exchange 2003.
